---
title: "Fallstudie"
author: "Sanja Perovic, Julia Zerrweck"
date: "8/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```


#1 Regression I
## a

```{r}
library(ISLR)
data(Auto)
fit <- lm(mpg ~ horsepower, data = Auto)
summary(fit)
```
### 1
- p Wert ist kleiner als 1, also kann die Nullhypothese verworfen werden. 
- bedeutet, dass es eine signifikante Beziehung gibt


### 2
```{r}
mean(Auto$mpg, trim = 0, na.rm = FALSE)
```

```{r}
(4.906/23.446)*100
```
The mean of mpg is 23.4459. The RSE of the lm.fit was 4.906 which indicates a percentage error of 20.9248%. The R-squared of the lm.fit was about 0.6059, meaning 60.5948% of the variance in mpg is explained by horsepower.


### 3
```{r}
cor <- cor.test(Auto$mpg, Auto$horsepower)

cor$estimate
```
negativ

### 4
nachschlagen

### 5
```{r}
predict(fit, data.frame(horsepower = 98), interval = "confidence")
```

### 6
```{r}
sqrt(mean(residuals(fit)^2))
```
Its just the square root of the mean of the squared residuals, like the name implies. It is the square root of the MSE.

```{r}
plot(Auto$horsepower, Auto$mpg, main = "scatterplot", xlab = "horsepower", ylab = "mpg", col = "red")
abline(fit, lwd = 3, col = "green")
```


```{r}
library(tidymodels)
library(skimr)
set.seed(42)
train <- sample(Auto, 3/4)
testdat  <- Auto[train]
traindat <- Auto[train]
```

```{r}
install.packages("gbm")
library(gbm)
library(MASS)
set.seed(42)
boost.dt <- gbm(mpg ~ horsepower, data = Auto, distribution = "gaussian", n.trees = 5000, interaction.depth = 4)
summary(boost.dt, plotit = FALSE)

```
```{r}
hp_plot <- plot(boost.dt, i = "horsepower")
gridExtra::grid.arrange(hp_plot, ncol = 2)
```





# 4 Gender Analysis
## 4.1.
```{r}
library(tidymodels)
library(skimr)
```


```{r}
# Fix the random numbers by setting the seed 
# This enables the analysis to be reproducible 
# when random numbers are used 
set.seed(42)

# Put 3/4 of the data into the training set 
data_split <- initial_split(responses, 
                            prop = 3/4)

# Create data frames for the two sets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```

